%------------------------
% Brent Pappas CV
% Template Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\setlength{\footskip}{4pt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-1pt} \\
      \textit{#3} & #4 \vspace{4pt} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\volunteeringItem}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-2pt} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Brent Pappas}} & Email: pappasbrent at gmail dot com\\
	\href{https://pappasbrent.com}{Portfolio: pappasbrent.com} & \\
	\href{https://github.com/pappasbrent}{Github: ~~github.com/pappasbrent} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
\resumeSubHeadingListStart{}
\resumeSubheading{}
{University of Central Florida (UCF)}
{Orlando, Florida}
{Bachelor of Science {-} Computer Science;  GPA\@: 3.849}
{August 2017 {-} May 2021}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:}
			Data Structures and Algorithms,
			Systems Software,
			Programming Languages,
			Discrete Structures}}}
\resumeSubheading{}
{UCF}
{Orlando, Florida}
{PhD {-} Computer Science;  GPA\@: 3.975}
{August 2021 {-} Present}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:}
			Analysis of Algorithms,
			Complexity Theory,
			Computer Architecture,
			Compiler Construction}}}
\resumeSubHeadingListEnd{}

%-----------SKILLS-----------------
\vspace{-5pt}
\section{Skills Summary}
\resumeSubHeadingListStart{}
\resumeSubItem{Languages}{~~~~~~Python 3, C/C++, Bash, HTML/CSS/JavaScript, Go, Haskell, Coq, SQL}
\resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, GitHub, LLVM/Clang}
\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Windows}
\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Writing, Communication, Time Management}
\resumeSubHeadingListEnd{}

%-----------WORK EXPERIENCE-----------------
\vspace{-5pt}
\section{Experience}
\resumeSubHeadingListStart{}

\resumeSubheading{}{Trail of Bits}{Remote}
{Summer Associate}{May 2023 {-} August 2023, December 2023}
\resumeItemListStart{}
\resumeItem{C Language Toolsmithing}
{Created Macroni, a C static analysis tool that combines Trail of Bits' tools
	PASTA and VAST to lower C preprocessor macros down to MLIR\@.
	Macroni is available at \href{https://github.com/trailofbits/macroni}{https://github.com/trailofbits/macroni}.}
\resumeItem{Peer-reviewed Development}
{Leveraged GitHub to push changes to company repos, submit code for code review,
	and finally merge changes into mainline branches.}
\resumeItem{Research Discussion}
{Exhibited research results and Macroni to team members and company CEO, Dan
	Guido, for advice and criticism.}
\resumeItemListEnd{}

\resumeSubheading{}{UCF}{In-person/Remote}
{Graduate Research Assistant}{July 2021 {-} Present}
\resumeItemListStart{}
\resumeItem{Research in Programming Languages}
{Stay up-to-date on the latest academic developments in programming languages.}
\resumeItem{Formal Methods}
{Formulate theorems about programming languages and try to prove them using
	the Coq Proof Assistant.}
\resumeItem{Implement Ideas}
{Implement research ideas in languages such as C++, e.g.\@ a Clang plugin for transforming C preprocessor macros to C functions.}
\resumeItem{Run Experiments}
{Write Python and Bash scripts to automate running experiments.}
\resumeItemListEnd{}

\resumeSubheading{}
{SP+}{In-person/Remote}
{Quality Assurance Coordinator}{September 2019 {-}  July 2021}
\resumeItemListStart{}
\resumeItem{Agile Software Development}
{Engaged in agile software development methods within a small team to QA test software before moving on to later phases of development.}
\resumeItem{Testing Automation}
{Refactored and wrote Python scripts to automate testing of various online user applications.}
\resumeItem{Mobile Application Testing}
{Tested company Android apps for compatibility with various versions of Android.}
\resumeItemListEnd{}

\resumeSubheading{}
{Student Academic Resource Center of UCF}{In-person}
{Peer Mentor}{August 2018 {-}  December 2019}
\resumeItemListStart{}
\resumeItem{Led Tutoring Sessions}
{Led Computer Science 1 and Object Oriented Programming tutoring sessions involving Socratic learning methods.}
\resumeItem{Faculty Collaboration}
{Collaborated with UCF teaching staff to enhance tutoring session quality.}
\resumeItem{Tutor Mentoring}
{Observed other tutors' sessions and provided feedback as to how they may improve their communication and tutoring skills.}
\resumeItemListEnd{}
\resumeSubHeadingListEnd{}

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart{}
\resumeItem{Macroni}
{A C static analysis tool that combines Trail of Bits' tools
	PASTA and VAST to lower C preprocessor macros down to MLIR.\@
	Macroni is available at \href{https://github.com/trailofbits/macroni}{https://github.com/trailofbits/macroni}.}
\resumeItem{Maki}
{C++ Clang plugin that analyzes hows C preprocessor macros affect the C AST\@.
Maki provides language porting tools information they can use to port macros to
target languages in a way that preserves not just macro behavior, but also macro
abstractions. Maki is the tool associated with 2024 ICSE paper,
\textit{Semantic Analysis of Macro Usage for Portability}, for which I am the lead-author.}
\vspace{2pt}
\resumeItem{Cpp2C}
{C++ Clang plugin that automatically transforms eligible C preprocessor macros into C functions.
	This enables other static analysis tools to analyze C programs without needing to preprocess them first and lose developer abstractions.}
\vspace{2pt}
\resumeItem{Chip-8 Emulator}
{An emulator of the Chip-8 virtual machine, written in C.}
\resumeSubHeadingListEnd{}

%-----------PUBLICATIONS-----------------
\vspace{-5pt}
\section{Publications}
\resumeSubHeadingListStart{}

\resumeSubItem{Semantic Analysis of Macro Usage for Portability}
{by Brent Pappas and Paul Gazzillo. International Conference on Software Engineering (ICSE), 2024. Acceptance rate - 234 / 1,051 (22\%). \url{https://doi.org/10.1145/3597503.3623323}}

\resumeSubItem{SugarC\@: Scalable Desugaring of Real-World Preprocessor Usage into Pure C}
{by Zach Patterson, Zenong Zhang, Brent Pappas, Shiyi Wei, and Paul Gazzillo. ICSE, 2022. Acceptance rate - 197 / 691 (28.5\%). \url{https://dl.acm.org/doi/10.1145/3510003.3512763}}
\resumeSubHeadingListEnd{}

%-----------Presentations-----------------
\vspace{-5pt}
\section{Presentations}
\resumeSubHeadingListStart{}
\resumeSubItem{Semantic Analysis of Macro Usage for Portability}
{Virtual presentation for Center of Academic Excellence in Cyber Research (CAE-R). 2023{-}08{-}31. \href{https://drive.google.com/file/d/1xCd34w54hs1iyaoXHz0MUkwlH-fP3HLo/view} {Recording link}}
\resumeSubHeadingListEnd{}

%-----------POSTERS-----------------
\vspace{-5pt}
\section{Posters}
\resumeSubHeadingListStart{}
\resumeSubItem{Cpp2C\@: Transforming C Preprocessor Macros to C Language Constructs}
{Presented a poster on transforming C preprocessor macros to C functions at the UCF 2022 Student Scholar Symposium.}
\resumeSubHeadingListEnd{}

%-----------AWARDS-----------------
\vspace{-5pt}
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
	\item {I was awarded the UCF FCI Student Scholarship in 2024 for the ability to demonstrate interest in interdisciplinary research, scholarship, and collaboration.}
	\vspace{-5pt}
	\item {I received my Bachelor's degree from UCF in 2021 with cum laude honors for having a cumulative GPA greater than 3.8.}
	\vspace{-5pt}
	\item {I was present on the UCF's Dean's List throughout all my undergraduate degree for scholastic achievement.}
	\vspace{-5pt}
	\item {I was admitted to the Burnett Honors College at UCF in 2017 for showing clear evidence of academic talent, motivation, intellectual curiosity and creativity.}
	\vspace{-5pt}
	\item {I received the Provost Scholarship from UCF in 2017 for outstanding academic performance in high school.}
\end{description}

%-----------CERTIFICATIONS-----------------
\vspace{-5pt}
\section{Certifications}
\begin{description}[font=$\bullet$]
	\item {\href{https://drive.google.com/file/d/1idZ5hhQQF4f-ZRQCBUplQTGU9YjS7fUs/view?usp=sharing}{Level 2 College Readiness and Learning Assessment (CRLA)} certified tutor.}
	      \vspace{-5pt}
	\item {UCF Student Enhancement Training (SET) program certified.}
\end{description}

%-----------VOLUNTEERING-----------------
\vspace{-5pt}
\section{Volunteer Experience}
\resumeSubHeadingListStart{}
\volunteeringItem{Camp Connect (at UCF)}
{Orlando, Florida {-} June 2021, June 2023}
\resumeItemListStart{}
\resumeItem{Teaching}
{Taught elementary, middle, and high school students the basics of computer
	programming in JavaScript.}
\resumeItemListEnd{}

\vspace{2pt}
\volunteeringItem{UCF CECS Senior Design Judge}
{Orlando, Florida {-} April 2022}
\resumeItemListStart{}
\resumeItem{Judging}
{Followed a given rubric to judge the quality of capstone projects for seniors of the College of Engineering and Computer Science.
	Criteria included presentation quality, project design quality, and creativity.}
\resumeItemListEnd{}

\vspace{2pt}
\volunteeringItem{UCF CECS Career Kickoff Alumni Mentor}
{Orlando, Florida {-} October 2022}
\resumeItemListStart{}
\resumeItem{Mentoring}
{Advised UCF freshmen on goal-setting, resume-building, and overall professionalism.}
\resumeItem{Job Application Prep}
{Conducted mock interview with UCF freshmen and provided tips on how to effectively search for jobs in their field.}
\resumeItemListEnd{}

\vspace{2pt}
\volunteeringItem{EuroSys 2023 Shadow Program Committee Member}
{Virtual {-} November-December 2022}
\resumeItemListStart{}
\resumeItem{Paper Review}
{Reviewed real paper submissions to EuroSys 2023.
	My Reviews were not considered by the actual program committee, but this experience gave me great insight into how conference papers are reviewed.}
\resumeItemListEnd{}

\vspace{2pt}
\volunteeringItem{OOPLSA 2024 Artifact Evaluation Committee Member}
{Virtual {-} January-February 2024}
\resumeItemListStart{}
\resumeItem{Artifact Review}
{Reviewed code artifacts associated with papers accepted to OOPLSA 2024.}
\resumeItemListEnd{}

\resumeSubHeadingListEnd{}

\end{document}
